setwd("C:/Users/anagh/OneDrive/SRH/Analytics3")
---
title: "Miles Per Gallon: An Analysis of the favourite data"
output: html_document
theme: cerulean
highlight: tango
author: "Anagha"
date: "`r Sys.Date()`"
---

# Notes

Modifying the header above might be somewhat tricky because of spaces and tabs which might muddle the yaml scanner.

For more information, see for example the comprehensive guide:

<https://bookdown.org/yihui/rmarkdown/>

```{r include=FALSE}
## above line: 'include=FALSE' does not include output in exported document.
## The following lines depends on your local settings and may be added
## automatically by your IDE
knitr::opts_chunk$set(echo = TRUE)
library("rmarkdown")
library("knitr")
```

# Outline

1.  Analyze the mpg data set with two statistical methods.
2.  Compare the results of both methods.
3.  Don't forget a descriptive analysis.
4.  Prepare a reproduce-able document of the analysis in Markdown or LaTeX.

# Descriptive Statistics

Here comes the descriptive stats

```{r }
#install.packages("tidyverse")
#library("dplyr")
#install.packages("ggplot2")
## your code starts here
db <- read.table("auto-mpg.data", fileEncoding = "UTF-8")
## assign column names
colnames(db)<-c("mpg", "cylinders", "displacement", "horsepower", "weight", "acceleration", "model_year", "origin", "car_name")
## convert horsepower char to numeric
db <- transform(db, horsepower = suppressWarnings(as.numeric(db$horsepower)))
## drop NA values
db <- na.omit(db)
## stats
summary(db)
```

# Statistical Model 1

Choice: linear regression Model

```{r}
#install.packages("shiny")
library(ggplot2)
print(ggplot(db, aes(displacement, mpg)) + geom_point()+ geom_smooth())
print(ggplot(db, aes(horsepower, mpg)) + geom_point()+ geom_smooth())
db_lm1 = lm(mpg ~ displacement, data = db)
summary(db_lm1)
##mpg = -0.06*displacement + 35.12, correlation = 0.64
db_lm2 = lm(mpg ~ weight, data = db)
summary(db_lm2)
predict(object = db_lm1,newdata = data.frame(displacement = c(300,400,50)))

```

# Statisical Model 2

Choice: Binary Tree Model

```{r}
#install.packages("rpart")
#install.packages("rpart.plot")
library(rpart)
library(rpart.plot)

smp_size <- floor(0.75 * nrow(db))

## set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(db)), size = smp_size)

train <- db[train_ind, ]
test <- db[-train_ind, ]

dbtree <- rpart(mpg ~ . -car_name, data = train, method = "anova")
print(rpart.plot(dbtree))
printcp(dbtree) # display the results
plotcp(dbtree) # visualize cross-validation results

#summary(dbtree) # detailed summary of splits

```



# Comparision
```{r}
db_lm <- lm(mpg ~ .  -car_name, data = db)
summary(db_lm)
#install.packages("olsrr")
library(olsrr)
ols_plot_cooksd_chart(db_lm)
ols_plot_cooksd_bar(db_lm)
ols_plot_resid_lev(db_lm)
op <- par(mfrow=c(2,3))
for(i in 1:6)
   plot(db_lm, which=i)
#no associiation btw resid and fitted values, which is good. because red line i almost a straight line. 
slm <- step(db_lm)
summary(slm)
slm$anova
slm
```

